### 2022-10-19 types.tex
more updates; things look dicey tbh

    \end{mathpar}\MPM{There's something fishy going on with varref-in; right now, you could use it and then immediately apply unfold to get a derivation which might not typecheck. We need to prove this is not actually a problem.}
    %\includegraphics{freehand-types}
  \label{fig:types}
  \caption{Types}
\end{figure}

We're not bothering with the oaklandish split right now, it's too
silly.  Open question if we need the relevance version of the rule, or
can remove the $:^r$ annotation and observe that the $[n]$ version is
only ever used with empty contexts for inputs to operators. Also worth
wondering if we're going to be in trouble overloading the [] syntax
here; time will tell. Types appear in figure \ref{fig:types}

>>>>

    {\inferrule[axoim-transform]{Γ ⊢ d ⇝ d' \\ C;Γ;d' ⊢ p : τ}{C;Γ;d ⊢ p : τ}}

    \end{mathpar}\MPM{There's something fishy going on with varref-in; right now, you could use it and then immediately apply unfold to get a derivation which might not typecheck. We need to prove this is not actually a problem.}
    %\includegraphics{freehand-types}
  \label{fig:types}
  \caption{Types: top-level}
\end{figure}
\begin{figure}
\begin{mathpar}

    {\inferrule[derivation-type-base]{}{Γ ⊢ d : τ}}

\end{mathpar}    
    \caption{Types: derivations }
    \label{fig:types2}
\end{figure}
\begin{figure}
\begin{mathpar}

{\inferrule[axoim-transform-base]{}{Γ ⊢ d ⇝ d'}}

\end{mathpar}    
    \caption{Types: axiom transformations }
    \label{fig:types3}
\end{figure}

Worth wondering if we're going to be in trouble overloading the $[]$ syntax here; time will tell. 
Types appear in figure \ref{fig:types}. 
Another concern is that we have a uhhh _lot_ of type systems in the mix at this point: 
we've got $C;Γ;d ⊢ p : τ$, $Γ ⊢ d : τ$, and $Γ ⊢ d ⇝ d'$.  
That's a lot more independent systems than we'd ideally  have.  Is there a way to collapse this back down?
